Efficient Handling of String-Number Conversion

### 2020-03-31 final-version/main.tex
update our response and explain more on the meaning of limited support

\begin{abstract}
String-number conversion is an important class of constraints needed for the symbolic execution of string-manipulating programs. In particular solving string constraints with string-number conversion  is necessary  for the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of these languages. However, the state-of-the-art constraint solvers have   limited support to this type of constraint. 
We propose to overcome these limitations with an approach that can efficiently support both string-number conversion and other common types of string constraints. Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
\end{abstract}

@@

An important class of string operations is  the string-number conversions.  While string length operations are sometimes well supported, converting a string $x$ to an integer $n$ (e.g., using the operation $n = \sti{x}$) or turning an integer value $n$ into its string form $x$ (e.g., using the operation $x = \its{n}$)  suffer from  limited support by the state-of-the-art string constraint solvers.

@@

Most of the state-of-the-art string constraint solvers provide   limited support to the combination of above constraints. Even for simple constraints like the above one, most solvers already fail to provide a correct answer. 
\changed{In Table~\ref{table:checkLuhn} of our evaluation (Section~\ref{section:evaluation}), CVC4 fails to solve constraints corresponding to checkLuhn of more than 6 loop iterations in 2 minutes, Z3 fails to solve the cases corresponding to 4,5,7, and 9 loop iterations, and Z3Str3 fails to solve  the case of 2 loop iterations.}

>>>>

\begin{abstract}
String-number conversion is an important class of constraints needed for the symbolic execution of string-manipulating programs. In particular solving string constraints with string-number conversion  is necessary for the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of these languages. \changed{However, solving this type of constraint is very challenging for the state-of-the-art solvers. They usually cannot handle formulae corresponding to longer program traces. 
We propose in this paper an approach that can efficiently support both string-number conversion and other common types of string constraints.} Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
\end{abstract}

@@

An important class of string operations is  the string-number conversions.  While string length operations are sometimes well supported, converting a string $x$ to an integer $n$ (e.g., using the operation $n = \sti{x}$) or turning an integer value $n$ into its string form $x$ (e.g., using the operation $x = \its{n}$) suffer from limited support \changed{(in terms of the scale of formulae they can handle)} by the state-of-the-art string constraint solvers.

@@

Most of the state-of-the-art string constraint solvers provide limited support to the combination of above constraints.
\changed{In Table~\ref{table:checkLuhn} of our evaluation (Section~\ref{section:evaluation}), CVC4 fails to solve constraints corresponding to checkLuhn of more than 6 loop iterations in 2 minutes, Z3 fails to solve the cases corresponding to 4,5,7, and 9 loop iterations, and Z3Str3 fails to solve  the case of 2 loop iterations.}
